SSA based global code motion of identical computations

### 2017-04-16 acmart-pacmpl-template.tex
taylor

Once the instructions have been classified into equivalence classes, we compute
for each group of equivalent instructions, a point in the program that is both
legal and profitable for the instructions to be moved to.

@@

After one iteration of algorithm runs through the entire function, it creates
more oppportunities for \emph{higher ranked} computations
\cite{rosen1988global}. Currently, this is a limitation of the \GVN{} analysis
pass, and so we rerun the code-hoisting algorithm until there are no more
instructions left to be hoisted.  Obviously, this is not the most optimal
approach and can be improved by ranking the computations \cite{rosen1988global},
or by improving the \GVN{} analysis to correctly number loads and dependent
instructions.

>>>>

Once the instructions have been classified into congruence classes
\cite{briggs1997} i.e., a set of instructions which compute the same value, we
compute for each group of congruent instructions, a point in the program that is
both legal and profitable for the instructions to be moved to.

@@

After one iteration of algorithm runs through the entire function, it creates
more oppportunities for \emph{higher ranked} computations
\cite{rosen1988global}. Currently, this is a limitation of the \GVN{} analysis
pass, and so we rerun the code-hoisting algorithm until there are no more
instructions left to be hoisted.  Obviously, this is not the most optimal
approach and can be improved by ranking the computations \cite{rosen1988global},
or by improving the \GVN{} analysis to correctly populate congruence classes.
